---
title: "Dr. Mehrkam SP20"
output: html_notebook
---


# 25 February 2020

## Loading in SD Data 

```{r, message = FALSE}
Kobe.Ian = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P1_Kobe&Ian')
Sally.Vanya = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P2_Sally&Vanya')
Rocky.Oaky = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P3_Rocky&Oaky')
Rosie.Carlie = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P4_Rosie&Carlie')
Koda.Ava = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P5_Koda&Ava')
Kodi.Kaia = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P6_Kodi & Kaia')
Dax.Fiona = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P7_Dax & Fiona')
Mason.Coffee = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P8_Mason&Coffee')
Gunner.Cato = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P9_Gunner&Cato')
Misha.Houston = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P10_Misha&Houston')
Rev.Blitz = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P11_Rev&Blitz')
Jude.Luna = read_excel('Play Exp 1 (SD) Data.xlsx', sheet = 'P12_Jude&Luna')
```

## Descriptives for the SD Data

### Dax & Fiona 

```{r, message = FALSE}
#library(mosaic)
favstats(~Dax.Fiona$`SD (s)`)
favstats(~Dax.Fiona$`S-Delta (s)`)
gf_line(Dax.Fiona$`SD (s)`~Dax.Fiona$Session...13) %>% gf_line(Dax.Fiona$`S-Delta (s)`~Dax.Fiona$Session...13, col = 'red') %>% gf_labs(title = 'Dax & Fiona SD Experiment', x = 'Session #', y = 'Time Played (Seconds)')
```

### Mason & Coffee

```{r}
favstats(~Mason.Coffee$`SD (Attention)`)
favstats(~Mason.Coffee$`S-Delta (No Attention)`)
gf_line(Mason.Coffee$`SD (Attention)`~Mason.Coffee$Session) %>% gf_line(Mason.Coffee$`S-Delta (No Attention)`~ Mason.Coffee$Session, col = 'red') %>% gf_labs(title = 'Mason & Coffee SD Experiment', x = 'Session #', y = 'Time Played (Seconds)')
```

### Gunner & Cato

```{r}
favstats(~Gunner.Cato$`SD (Attention)`)
favstats(~Gunner.Cato$`S-Delta (No Attention)`)
gf_line(Gunner.Cato$`SD (Attention)`~ Gunner.Cato$Session) %>% gf_line(Gunner.Cato$`S-Delta (No Attention)`~ Gunner.Cato$Session, color = 'red') %>% gf_labs(title = 'Gunner & Cato SD Experiment', x = 'Session #', y = 'Time Played (Seconds)')
```

### Misha & Houston

```{r}
favstats(~Misha.Houston$`SD (Attention)...3`)
favstats(~Misha.Houston$`S-Delta (No Attention)...4`)
gf_line(Misha.Houston$`SD (Attention)...3`~ Misha.Houston$Session...2) %>% gf_line(Misha.Houston$`S-Delta (No Attention)...4`~Misha.Houston$Session...2, color = 'red') %>% gf_labs(title = 'Misha & Houston SD Experiment', x = 'Session #', y = 'Time Played (Seconds)')
```

### Rev & Blitz

```{r}
favstats(~Rev.Blitz$`SD (Attention)`)
favstats(~Rev.Blitz$`S-Delta (No Attention)`)
gf_line(Rev.Blitz$`SD (Attention)`~ Rev.Blitz$Session) %>% gf_line(Rev.Blitz$`S-Delta (No Attention)`~ Rev.Blitz$Session, color = 'red') %>% gf_labs(title = 'Rev & Blitz SD Experiment', x = 'Session #', y = 'Time Played (Seconds)')
```

### Jude & Luna

```{r}
favstats(~Jude.Luna$`SD (Attention)`)
favstats(~Jude.Luna$`S-Delta (No Attention)`)
gf_line(Jude.Luna$`SD (Attention)`~Jude.Luna$Session) %>% gf_line(Jude.Luna$`S-Delta (No Attention)`~Jude.Luna$Session, color = 'red') %>% gf_labs(title = 'Jude & Luna SD Experiment', x = 'Session #', y = 'Time Played (Seconds)')
```



# 27 February 2020 

## Loading in EO Data

```{r}
Dax.Fiona.E0 = read_excel('Play Exp 2 (EO) Data.xlsx', sheet = 'P7_Dax & Fiona')
Misha.Houston.EO = read_excel('Play Exp 2 (EO) Data.xlsx', sheet = 'P8_Misha&Houston')
Gunner.Cato.EO = read_excel('Play Exp 2 (EO) Data.xlsx', sheet = 'P9_Gunner&Cato')
Coffee.Mason.EO = read_excel('Play Exp 2 (EO) Data.xlsx', sheet = 'P10_Coffee&Mason')
Rev.Blitz.EO = read_excel('Play Exp 2 (EO) Data.xlsx', sheet = 'P11_Rev&Blitz')
```

## Descriptives for EO Data

### Dax & Fiona


## Loading in Reinforced Data

```{r}
Dax.Fiona.Rein = read_excel('Play Exp 3 (Reinforcer) Data Edited.xlsx', sheet = 'P7_Dax & Fiona')
Misha.Houston.Rein = read_excel('Play Exp 3 (Reinforcer) Data Edited.xlsx', sheet = 'P8_Misha&Houston')
Gunner.Cato.Rein = read_excel('Play Exp 3 (Reinforcer) Data Edited.xlsx', sheet = 'P9_Gunner&Cato')
Coffee.Mason.Rein = read_excel('Play Exp 3 (Reinforcer) Data Edited.xlsx', sheet = 'P10_Coffee&Mason')
Rev.Blitz.Rein = read_excel('Play Exp 3 (Reinforcer) Data Edited.xlsx', sheet = 'P11_Rev&Blitz')
```


## Descriptives for Reinforced Data

### Dax & Fiona

```{r}
favstats(Dax.Fiona.Rein$`Attention Control`)
favstats(Dax.Fiona.Rein$`Attention Test`)
favstats(Dax.Fiona.Rein$Alone)
gf_line(Dax.Fiona.Rein$`Attention Control`~Dax.Fiona.Rein$Session) %>% gf_line(Dax.Fiona.Rein$`Attention Test`~ Dax.Fiona.Rein$Session, color = 'red') %>% gf_line(Dax.Fiona.Rein$Alone~Dax.Fiona.Rein$Session, color = 'blue') %>% gf_labs(title = 'Dax & Fiona Reinforced Experiment', x = 'Session #', y = 'Time Played (Seconds)')
```

# 3 March 2020 

### Misha & Houston

```{r}
favstats(~Misha.Houston.Rein$`Attention Control`)
favstats(~Misha.Houston.Rein$`Attention Test`)
favstats(~Misha.Houston.Rein$Alone)
gf_line(Misha.Houston.Rein$`Attention Control`~Misha.Houston.Rein$Session) %>% gf_line(Misha.Houston.Rein$`Attention Test`~Misha.Houston.Rein$Session, color = 'red') %>% gf_line(Misha.Houston.Rein$Alone~Misha.Houston.Rein$Session, color = 'blue') %>% gf_labs(title = 'Misha & Houston Reinforcer Experiment', x = 'Session #', y = 'Time Played (Seconds)')
```

### Gunner & Cato

```{r}
favstats(~Gunner.Cato.Rein$`Attention Control`)
favstats(~Gunner.Cato.Rein$`Attention Test`)
favstats(~Gunner.Cato.Rein$Alone)
gf_line(Gunner.Cato.Rein$`Attention Control`~Gunner.Cato.Rein$Session) %>% gf_line(Gunner.Cato.Rein$`Attention Test`~Gunner.Cato.Rein$Session, color = 'red') %>% gf_line(Gunner.Cato.Rein$Alone~Gunner.Cato.Rein$Session, color = 'blue') %>% gf_labs(title = 'Gunner & Cato Reinforcer Experiment', x = 'Session #', y = 'Time Played (Seconds)')
```

### Coffee & Mason 

```{r}
favstats(~Coffee.Mason.Rein$`Attention Control`)
favstats(~Coffee.Mason.Rein$`Attention Test`)
favstats(~Coffee.Mason.Rein$Alone)
gf_line(Coffee.Mason.Rein$`Attention Control`~Coffee.Mason.Rein$Session) %>% gf_line(Coffee.Mason.Rein$`Attention Test`~Coffee.Mason.Rein$Session, color = 'red') %>% gf_line(Coffee.Mason.Rein$Alone~Coffee.Mason.Rein$Session, color = 'blue') %>% gf_labs(title = 'Coffee & Mason Reinforcer Experiment', x = 'Session #', y = 'Time Played (Seconds)')
```

### Rev & Blitz

```{r}
favstats(~Rev.Blitz.Rein$`Attention Control`)
favstats(~Rev.Blitz.Rein$`Attention Test`)
favstats(~Rev.Blitz.Rein$Alone)
gf_line(Rev.Blitz.Rein$`Attention Control`~Rev.Blitz.Rein$Session) %>% gf_line(Rev.Blitz.Rein$`Attention Test`~Rev.Blitz.Rein$Session, color = 'red') %>% gf_line(Rev.Blitz.Rein$Alone~Rev.Blitz.Rein$Session, color = 'blue') %>% gf_labs(title = 'Rev & Blitz Reinforcer Experiment', x = 'Session #', y = 'Time Played (Seconds)') 
```

## Descriptives for EO Dataset

### Dax & Fiona

```{r}
par(mfrow = c(1,2))
barplot(c(17,23,	0,	198), names.arg = c('0', '30', '120', '>360'), ylim = c(0,300), xlab = 'Owner Deprivation (min)', ylab = 'Time Played (Seconds)',col = rainbow(4))
barplot(c(0	,4	,0	,192), names.arg = c('0', '30', '120', '>360'), ylim = c(0,300), xlab = 'Owner Deprivation (min)', ylab = 'Time Played (Seconds)',col = rainbow(4))
```

### Misha & Houston

```{r}
par(mfrow = c(1,2))
barplot(c(26,	99,	4,	71), names.arg = c('0', '30', '120', '>360'), ylim = c(0,300), xlab = 'Owner Deprivation (min)', ylab = 'Time Played (Seconds)',col = rainbow(4))
barplot(c(3,	0,	9,	92), names.arg = c('0', '30', '120', '>360'), ylim = c(0,300), xlab = 'Owner Deprivation (min)', ylab = 'Time Played (Seconds)',col = rainbow(4))

```

### Gunner & Cato

```{r}
par(mfrow = c(1,2))
barplot(c(115	,156	,193,	49), names.arg = c('0', '30', '120', '>360'), ylim = c(0,300), xlab = 'Owner Deprivation (min)', ylab = 'Time Played (Seconds)',col = rainbow(4))
barplot(c(4	,106,	119,	203), names.arg = c('0', '30', '120', '>360'), ylim = c(0,300), xlab = 'Owner Deprivation (min)', ylab = 'Time Played (Seconds)',col = rainbow(4))

```

### Coffee & Mason

```{r}
par(mfrow = c(1,2))
barplot(c(83	,22,	141	,6), names.arg = c('0', '30', '120', '>360'), ylim = c(0,300), xlab = 'Owner Deprivation (min)', ylab = 'Time Played (Seconds)',col = rainbow(4))
barplot(c(12,	2	,0	,1), names.arg = c('0', '30', '120', '>360'), ylim = c(0,300), xlab = 'Owner Deprivation (min)', ylab = 'Time Played (Seconds)',col = rainbow(4))

```

### Rev & Blitz

```{r}
par(mfrow = c(1,2))
barplot(c(5	,3	,8	,14), names.arg = c('0', '30', '120', '>360'), ylim = c(0,300), xlab = 'Owner Deprivation (min)', ylab = 'Time Played (Seconds)',col = rainbow(4))
barplot(c(1	,1	,1	,14), names.arg = c('0', '30', '120', '>360'), ylim = c(0,300), xlab = 'Owner Deprivation (min)', ylab = 'Time Played (Seconds)',col = rainbow(4))
```

